---
title: "Bibliography"
date: "02/05/2025"
date-modified: today
format: html
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(dlstats)
library(plotly)
knitr::opts_chunk$set(
  fig.align = "center",
  # This for default device
  out.width = "16cm",
  # This two for high quality charts:
  fig.dim = c(16, 9)*0.4
)
```


Members of RTUG have contributed to the following topics:

# {{< bi box >}} CRAN Packages

* [ADAS Utils](https://cran.r-project.org/package=adas.utils){target="_blank"}---Design of Experiments
* [noisyCE2](https://cran.r-project.org/package=noisyCE2){target="_blank"}---Cross-Entropy Optimisation of Noisy Functions

```{r}
#| echo: false
pp <- cran_stats(c("adas.utils", "noisyCE2")) %>% 
  ggplot(aes(x=end, y=downloads, group=package, color=package)) +
  geom_line() +
  scale_x_date(date_labels="%Y",
               date_breaks="1 year", 
               date_minor_breaks="3 months") +
  labs(x="Date", 
       y="Monthly downloads", 
       color="Package", 
       title="RTUG-contributed packages")

ggplotly(pp)
```

# {{< bi book >}} Books

* Agresti A., C. Franklin, B. Klingenberg (2025) *Statistica --- l’arte e la scienza d’imparare dai dati* (quinta edizione), Pearson Italia, Milano (a cura di G. Espa, R. Micciolo, D. Giuliani, M.M. Dickson). ISBN: 9788891931894.
* Bosetti, P. (2022) *[Fondamenti di statistica](https://www.amazon.it/Fondamenti-statistica-misure-lanalisi-industriale/dp/8833595188/ref=sr_1_1?__mk_it_IT=ÅMÅŽÕÑ&crid=130DECQXCJAUU&dib=eyJ2IjoiMSJ9.JkZQh7pdSELYBbubl0AOoP8hMF5WE4YX2v5WcqzrSI1PkWPXwJATHdzq_sXG3tdeY5ZCf-riK7MHsBVIsOgfzw.moxkeVLCwEDMXtkOTAo-98QTge2OlqYC6M-VW7sYvgY&dib_tag=se&keywords=paolo+bosetti&qid=1738757933&sprefix=paolo+bosetti%2Caps%2C131&sr=8-1){target="_blank"} --- Per le misure e l’analisi dati in ambito industriale. Con esempi in GNU-R*. Libreriauniversitaria.it. ISBN: 978-8833595188.
* Micciolo R., L. Canal, G. Espa (2021) *Probabilità e modelli – Teoria e pratica con R*, Apogeo Education, Maggioli Editore, Santarcangelo di Romagna (RN). ISBN: 978-88-916-4935-5.
* Espa G., R. Micciolo (2014) *Problemi ed Esperimenti di Statistica con R*, Apogeo Education, Maggioli Editore, Santarcangelo di Romagna (RN). ISBN: 8838786105.
* Bee M, F. Santi (2013) *Finanza quantitativa con R*, Apogeo Education, Maggioli Editore, Santarcangelo di Romagna (RN). ISBN: 8838787041.
* R. Micciolo, G. Espa, L. Canal (2013) *Ricerca con R – Metodi di inferenza statistica*, Apogeo Education, Maggioli Editore, Santarcangelo di Romagna (RN). ISBN: 8838787003.
* Espa G., R.  Micciolo (2012) *Analisi esplorativa dei dati con R*, Apogeo Education, Maggioli Editore, Santarcangelo di Romagna (RN). ISBN 8838786853.

# {{< fa regular newspaper >}} Papers

* Santi F., M.M. Dickson, G. Espa, D. Giuliani (2022) *plot3logit: Ternary Plots for Interpreting Trinomial Regression Models*, Journal of Statistical Software, Code Snippets, 103 (1), 1–27. DOI: 10.18637/jss.v103.c01.
* Giuliani D., M.M. Dickson, G. Espa (2015) *Teaching statistics in the context of social foresight. An applied approach based on the use of an open-source software*, On the Horizon, 23, 2, 140–148. DOI: 10.1108/OTH-02-2015-0010.
* Canal L., Micciolo R. (2008) *The proportional means regression model for the analysis of recurrent event data*. BioMedical Statistics and Clinical Epidemiology, 2:2, 157-169 ([pdf here](http://hostingwin.unitn.it/micciolo/pmr/Canal_Micciolo%20(web).pdf)).
* Canal L., Micciolo R. (2014) *The chi-square controversy: what if Pearson had R?*. Journal of Statistical Computation and Simulation, 84:5, 1015-1021. DOI: 10.1080/00949655.2012.737793
* Decarli A., La Vecchia C., Malvezzi M., Micciolo R. (2014) *An R package for fitting age, period and cohort models*. Epidemiology Biostatistics and Public Health, 11:4, e9977-1 – e9977-12. DOI: 10.2427/9977 ([pdf here](https://riviste.unimi.it/index.php/ebph/article/view/17936/15736>)).
* Fedrizzi G., Canal L., Micciolo R. (2022). *UEFA EURO 2020: An exciting match between football and probability*. Teaching Statistics, 44:3, 119-125. DOI: 10.1111/test.12315 ([pdf here](https://onlinelibrary.wiley.com/doi/10.1111/test.12315)).





